### 2013-03-26 doc/final_report/implementation.tex
hit the 10k words barrier

During the development of Partridge, the structure of the SQL database

>>>>

During the development of Partridge, the structure of the SQL database used to
store the papers changed a lot due to modifications to the ORM modules as
discussed above. These structural changes meant that the production database at
\url{http://farnsworth.papro.org.uk/} and the development database were not
compatible and that updates to the code on the development server would break
the application on the prodution server unless the database structure was also
updated.
